Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure 15
Updated Figure 11

free(error_plot_pbmc) + wrap_plots(nldr1c, nldr2c, nldr3c, nldr4c,
           nldr5c, nldr6c, nldr7c, nldr8c, ncol = 2)
```

@@

img_right_top <- c(868, 1465, 1787, 1788, 1789)

@@

img_middle <- c(130, 2091, 7795, 7796, 7797)

@@

img_right_bottom <- c(2035, 7708, 7710, 7711, 7712)

@@

img_error_outside <- c(999, 3650, 4916, 4917, 4918)

>>>>

design <- "
AABB
AABB
AABB
"

# Put error plot in area A, and wrap_plots in area B
error_plot_pbmc + 
  wrap_plots(nldr1c, nldr2c, nldr3c, nldr4c,
             nldr5c, nldr6c, nldr7c, nldr8c, ncol = 2) +
  plot_layout(design = design)
```

@@

img_right_top <- c(868, 1465, 1787, 2006, 4314)

@@

img_middle <- c(130, 2091, 7795, 163, 77)

@@

img_right_bottom <- c(2035, 7708, 7710, 4134, 5006)

@@

img_error_outside <- c(999, 3650, 4916, 2964, 5622)
